Deep Learning

### 2015-01-31 deepreview.tex
higher-resolution figures, removed old bp figure, rewrote preface

Deep neural networks that learn to represent data using layers
of increasing abstract features have dramatically improved the
state-of-the-art for speech recognition, object recognition, object
detection, predicting the activity of drug molecules, and many other
tasks. Deep learning discovers intricate structure in large datasets
by using the backpropagation algorithm to compute error-derivatives
for the weights that define each layer of feature detectors and then
repeatedly changing these weights in proportion to their derivatives
averaged over small batches of training examples.  Deep recurrent
neural networks, in which each layer also receives input from its own
state at the previous time-step, can now generate good captions for
images and are competitive for language translation.

>>>>

Deep neural networks that learn to represent data using layers of
increasingly abstract features have dramatically improved the
state-of-the-art for speech recognition, object recognition, object
detection, predicting the activity of drug molecules, and many other
tasks. Deep learning discovers intricate structure in large datasets by
using the {\em backpropagation algorithm} to compute how the neural network
should change in order to make less errors.  Deep {\em recurrent neural
  networks} can process a sequence of inputs and produce a sequence of
outputs and can now generate good captions for images and are competitive
for language translation.
